Target Markdown

### 2024-04-02 _targets.Rmd
Begin to analyse interference simulations

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("no_rerun", "non_allo_no_rerun", "rerun", "no_rerun_short",
  "no_rerun_no_disconnected")
    )
```

@@

```{targets raw-data}
list(
  tar_target(sim_list, {
    sim_files <- list.files(here("res", "simCSZenrich"))
    map(sim_files,
      function (x) {
        open_dataset(here::here("res", "simCSZenrich", x),
          format = "arrow") %>%
        collect()
      })
}
    ),
  tar_target(simZ_prep,
    map_dfr(sim_list,
      function (x) {
        x %>%
          # Remove simulation that have failed to run
          filter(!is.na(richness)) %>%
          # Transform back interaction strength into matrices
          mutate(across(where(is.list), as.list)) %>%
          mutate(across(c(int_strength, max_int),
              ~map2(.x, S,
                function(y, rich) {
                  matrix(y, nrow = rich)
                }
              )
          )
            ) %>%
          # Get matrix of alive species
          mutate(max_int_alive  = map2(max_int, bm_sp,
              function(mat, bm) {
                mask <- bm > 10^-6
                mat[mask, mask, drop = FALSE]
              }
            )
          )
      }
    )
    ),
  tar_target(simZ,
    simZ_prep %>%
      mutate(
        persistence = richness / S,
        async = 1 / sync,
        stab_pop = 1 / avg_cv_sp,
        ct_alive = map_dbl(max_int_alive,
          ~ifelse(sum(.x) == 0, 0,
            sum(.x > 0) / ((ncol(.x))^2))),
        bm_sp_alive = map(bm_sp, ~.x[.x > 10^-6]),
        tlvl_alive = map2(tlvl, bm_sp, ~.x[.y > 10^-6]),
        max_tlvl_alive = map_dbl(tlvl_alive, max),
        w_avg_tlvl_alive = map2_dbl(tlvl_alive, bm_sp_alive,
          ~sum(.x * (.y / sum(.y)))
          ),
        max_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, max(.x[.x > 0]))
          ),
        avg_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, mean(.x[.x > 0]))
          ),
        sd_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) <= 1, 0, sd(.x[.x > 0]))
          ),
        cv_max_int_alive = sd_max_int_alive / avg_max_int_alive,
        inv_sd_max_int_alive = 1 / sd_max_int_alive,
        gini_max_int_alive = map_dbl(max_int_alive,
          ~ifelse(length(.x[.x > 0]) == 0, 0, gini(.x[.x > 0])))
      )
  )
)
```

```{targets sim_rho, tar_simple = TRUE}
simZ %>%
  filter(ct_alive != 0, avg_max_int_alive != 0) %>%
  mutate(across(c(async, sync, stab_pop, avg_cv_sp, stab_com, richness, avg_max_int_alive, gini_max_int), log, , .names = "log_{.col}")) %>%
  mutate(
    log1_avg_max_int_alive = log(avg_max_int_alive + 1),
    productivity_f = factor(productivity)
    ) %>%
  select(c(
      ct_alive, log_richness, max_tlvl_alive, Z, rho,
      gini_max_int, avg_max_int_alive, log1_avg_max_int_alive, env_stoch,
      log_stab_com, log_sync, log_async, log_stab_pop, log_avg_cv_sp, productivity, productivity_f,
      persistence)
  )
```

```{targets sim_rho_scaled, tar_simple = TRUE}
sim_rho %>%
  mutate(across(where(is.double), ~scale(.x)[,1]))
```

```{targets rho_model}
list(
  tar_target(formula_fixed_rho, formula_mod_rho_fixed_effect()),
  tar_target(formula_rand_rho, "(1 | Z)"),
  tar_target(mod_rho, map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
      sim_rho)
  }
  )),
  tar_target(coef_mod_rho, map_dfr(mod_rho, ~model2tibble(.x))),
  tar_target(r2_mod_rho, map_dfr(mod_rho, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
  mutate(response = var_replacement()[response])),
  tar_target(p_mod_rho, plot_effect_type(coef_mod_rho)),
  tar_target(mod_rho_scaled, map(setNames(
    c("log_stab_com", "log_stab_pop", "log_async"),
    c("log_stab_com", "log_stab_pop", "log_async")
    ),
  function (x) {
    glmmTMB(formula(paste0(x, " ~ ", formula_fixed_rho, " + ", formula_rand_rho)),
      sim_rho_scaled)
  }
)
    ),
  tar_target(coef_mod_rho_scaled, map_dfr(mod_rho_scaled, ~model2tibble(.x))),
  tar_target(r2_mod_rho_scaled,
    map_dfr(mod_rho_scaled, ~as.data.frame(r2_nakagawa(.x)), .id = "response") %>%
      mutate(response = var_replacement()[response])),
  tar_target(colin_rho, performance::check_collinearity(lm(formula(str_replace_all(paste0("log_stab_com ~ ", formula_fixed_rho), "(\\*|:)", "+")),
  sim_rho_scaled))),
    tar_target(p_mod_rho_scaled, plot_effect_type(coef_mod_rho_scaled))
)
```

```{targets pred_rho}
tar_target(pred_rho,
  {
  pred_rho <- list(
    log_richness = c(log(1), log(5), log(10), log(20), log(30), log(50)),
    ct_alive = c(.05, .10, .40),
    rho = c(0, .5, 1),
    log1_avg_max_int_alive = c(log(0.2 + 1), round(log(.81 + 1), 1), round(log(5.65 + 1), 1)),
    env_stoch = .5,
    productivity = c("basic", "enrichment"),
    Z = 100
    ) %>% expand.grid() %>%
  filter(
    !(log1_avg_max_int_alive == 0 & ct_alive != 0 | ct_alive == 0 & log1_avg_max_int_alive != 0)
  )
  pred_rho$log_stab_com <- predict(mod_rho[["log_stab_com"]], newdata = pred_rho)
  pred_rho
  }
)
```

# New simulation

```{targets raw_sim}
list(
  tar_target(sim_fw, sim_fw_rerun),
  tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
  tar_target(sim_fw_df, as.data.frame(sim_fw))
  )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + resp_div, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
    #filter(abs(Std.Estimate) > 0.1)# %>%
    #  mutate(
    #    Response = var_replacement()[Response],
    #    Predictor = var_replacement()[Predictor]
    #  ) %>%
    }),
  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
  tar_target(sem_eff, {
    readRDS(sim_eff_file)
    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

```{targets group-all-analysis}
list(
  tar_target(sem_simplified_tot,
    tibble(
      sim_type = c(
        "no_rerun",
        "non_allo_no_rerun",
        "rerun",
        "no_rerun_short",
        "no_rerun_no_disconnected"),
      eff = list(
        sem_simplified_eff_tab_no_rerun,
        sem_simplified_eff_tab_non_allo_no_rerun,
        sem_simplified_eff_tab_rerun,
        sem_simplified_eff_tab_no_rerun_short,
        sem_simplified_eff_tab_no_rerun_no_disconnected
        ),
      rsq = list(
        sem_simplified_rsquared_no_rerun,
        sem_simplified_rsquared_non_allo_no_rerun,
        sem_simplified_rsquared_rerun,
        sem_simplified_rsquared_no_rerun_short,
        sem_simplified_rsquared_no_rerun_no_disconnected
        ),
      collinearity = list(
        sem_simplified_collinearity_no_rerun,
        sem_simplified_collinearity_non_allo_no_rerun,
        sem_simplified_collinearity_rerun,
        sem_simplified_collinearity_no_rerun_short,
        sem_simplified_collinearity_no_rerun_no_disconnected
        ),
    )
  ),
  tar_target(sem_simplified_eff_tab_tot,
    sem_simplified_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_simplified_eff_tab_tot,
    sem_simplified_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      #sae_even = lm(sae_even ~ richness, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_main_text_model_list,
    list(
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
  ),
  tar_target(sem_main_text, {
    ti <- as.psem(sem_main_text_model_list)
    #update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_collinearity,
    sem_simplified_collinearity_no_rerun
    ),
  tar_target(sem_simplified_rsquared,
    sem_simplified_rsquared_no_rerun %>%
      mutate(
      Response = var_replacement()[Response],
      R.squared = round(R.squared, 2)
      ) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term],
        VIF = round(VIF, 2),
        SE_factor = round(SE_factor, 2)
        ) %>%
        rename(Response = response)
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_no_rerun)
)
```

```{r, eval = FALSE}
tar_load(sem_main_text)
m <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)
ti <- as.psem(m)
update(ti, avg_omnivory %~~% w_avg_tlvl)
summary(ti)
```

```{targets model-to-pred}
  tar_target(model_fw_stab,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw, across(c(stab_com, richness), log))
      )),
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async, richness), log)
      ))
        )),
        pattern = stab_com_part_var
  tar_target(model_fw_stab_scaled,
    glmmTMB(formula_stab_fw_model(
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
      data = sim_fw %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, richness,
              env_stoch, resp_div, Z,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
      data = sim_fw %>%
        mutate(across(c(stab_com, richness), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, h,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        ))),
        pattern = stab_com_part_var
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  tar_target(model_fw_stab_scaled_coeff,
    confint(tar_read(model_fw_stab_scaled), level = 0.95) %>%
      as.data.frame() %>%
      rownames_to_column("term") %>%
      as_tibble() %>%
      mutate(term = str_replace(term, "cond\\.", ""))
  tar_target(pred_data, {
    to <- list(
      richness = log(seq(1, 30, 1)),
      ct_alive = c(.05, .10, .30),
      resp_div = 1 - c(0, .75, 1),
      avg_int_strength = c(.01, .02, .05, .1),
      env_stoch = c(.1, .6),
      w_avg_tlvl = c(1.0, 1.5, 2.3),
      Z = c(1, 10, 100),
      h = c(2, 3),
      fw_id = NA) %>% expand.grid()
    ti <- predict(model_fw_stab,
      se.fit = TRUE, re.form = NA,
      newdata = to)
    to$stab_com <- ti$fit
    to$stab_com_se <- ti$se.fit
    to
    }),
  tar_target(fixed_effect_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(
  error = "null",
  packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra")
)
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("csc_rerun", "csc_kno", "csc_non_allo", "csc_rebuild")
    )
```

@@

@@

```{targets sem-process}
list(
  tar_target(sim_fw, sim_fw_csc_rerun),
  tar_target(sim_fw_sem,
    sim_fw %>%
      as.data.frame() %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_eff,  sem_main_text_eff_csc_rerun),
  tar_target(sem_eff_tab, sem_main_text_eff_tab_csc_rerun),
  tar_target(sem_eff_coeff, sem_main_text_eff_tab_csc_rerun),
  tar_target(tab_sem_coeff,
    sem_main_text_coeff_csc_rerun %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity, sem_main_text_collinearity_csc_rerun),
  tar_target(sem_rsquared, sem_main_text_rsquared_csc_rerun),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

```{r, eval = FALSE}
library(targets)
tar_load_globals()
tar_load(starts_with("sim_fw_csc"))
sim_fw_csc_rerun
sim_fw_csc_rebuild
sim_fw_csc_kno
sim_fw_csc_non_allo
sim_fw_csc_non_allo
```

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_file, here::here("data", paste0("sem_simplified_", names)), format = "file"),
  tar_target(sem_simplified, { readRDS(sem_simplified_file) }),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff)),
  tar_target(sem_main_text_file, here::here("data", paste0("sem_main_text_", names)), format = "file"),
  tar_target(sem_main_text, { readRDS(sem_main_text_file) }),
  tar_target(sem_main_text_eff_file, here::here("data", paste0("sem_main_text_eff_", names)), format = "file"),
  tar_target(sem_main_text_eff, { readRDS(sem_main_text_eff_file) }),
  tar_target(sem_main_text_collinearity_file, here::here("data", paste0("sem_main_text_collinearity_", names)), format = "file"),
  tar_target(sem_main_text_collinearity, { readRDS(sem_main_text_collinearity_file) }),
  tar_target(sem_main_text_rsquared_file, here::here("data", paste0("sem_main_text_rsquared_", names)), format = "file"),
  tar_target(sem_main_text_rsquared, { readRDS(sem_main_text_rsquared_file) }),
  tar_target(sem_main_text_coeff_file, here::here("data", paste0("sem_main_text_coeff_", names)), format = "file"),
  tar_target(sem_main_text_coeff, { readRDS(sem_main_text_coeff_file) }),
  tar_target(sem_main_text_eff_tab, from_semEff_to_table(sem_main_text_eff))
)
```

```{targets group-all-analysis, eval = FALSE}
list(
  tar_target(sem_main_text_tot,
    tibble(
      sim_type = c(
        "rerun",
        "non_allo",
        "rebuild",
        "no_rerun_short",
        "kno"),
      eff = list(
        sem_main_text_eff_tab_csc_rerun,
        sem_main_text_eff_tab_csc_non_allo,
        sem_main_text_eff_tab_csc_rebuild,
        sem_main_text_eff_tab_csc_kno
        ),
      rsq = list(
        sem_main_text_rquared_csc_rerun,
        sem_main_text_rquared_csc_non_allo,
        sem_main_text_rquared_csc_rebuild,
        sem_main_text_rquared_csc_kno
        ),
      collinearity = list(
        sem_main_text_collinearity_csc_rerun,
        sem_main_text_collinearity_csc_non_allo,
        sem_main_text_collinearity_csc_rebuild,
        sem_main_text_collinearity_csc_kno
        ),
    )
  ),
  tar_target(sem_main_text_eff_tab_tot,
    sem_main_text_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_main_text_eff_tab_tot,
    sem_main_text_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_csc_rerun),
  tar_target(sem_main_text_eff_tab, sem_main_text_eff_tab_csc_rerun)
)
```

```{r, eval = FALSE}
tar_load(sem_main_text)
tar_load(sim_fw_sem)

m <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)

m2 <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)

ti <- as.psem(m)
ti2 <- as.psem(m2)
#update(ti, avg_omnivory %~~% w_avg_tlvl)
summary(ti)
summary(ti2)
tar_load(sim_fw_sem)

m3 <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + c + Z + resp_div, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + c + Z + env_stoch + resp_div, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  cpe_env = lm(cpe_env ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div + c + Z + env_stoch, sim_fw_sem),
  #cpe = lm(cpe ~ cpe_env + cpe_int, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)
summary(as.psem(m3))

```{targets model-to-pred}
list(
  tar_target(stab_com_part_var, c("stab_com", "pop_stab", "async")),
  tar_target(model_fw_stab_comp,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
      resp = stab_com_part_var,
      rand_effect = TRUE,
      term_to_del = "richness : resp_div : Z +"),
      data = mutate(sim_fw,
      across(c(stab_com, pop_stab, async, richness), log)
      ))
        )),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled,
    tibble(
      response = stab_com_part_var,
      model = list(glmmTMB(formula_stab_fw_model(
        resp = stab_com_part_var,
        rand_effect = TRUE,
        term_to_del = "richness : resp_div : Z +"
        ),
      data = sim_fw %>%
        mutate(across(c(stab_com, richness, pop_stab, async), log)) %>%
        mutate(across(c(sim_id, fw_id), as.factor)) %>%
        mutate(
          across(c(stab_com, pop_stab, async, richness,
              env_stoch, resp_div, Z, c,
              ct_alive, w_avg_tlvl, avg_int_strength, avg_omnivory),
            ~scale(.x)[, 1])
        )
        ))),
        pattern = stab_com_part_var
  ),
  tar_target(model_fw_stab_comp_scaled_coeff,
    model_fw_stab_comp_scaled %>%
      mutate(
        coeff = map(model, function(x) {
          confint(x, level = 0.95) %>%
          as.data.frame() %>%
          rownames_to_column("term") %>%
          as_tibble() %>%
          mutate(term = str_replace(term, "cond\\.", ""))
        })
      ) %>%
      select(-model)
  ),
  tar_target(fixed_effect_fw_stab_comp,
    model_fw_stab_comp %>%
      mutate(
      fix_effect = map(model, ~fixef(.x)$cond)
      ) %>%
      select(-model)
  ),
  tar_target(default_variable_values_pred,
    c(
      "resp_div" = mean(sim_fw$resp_div),
      "env_stoch" = mean(sim_fw$env_stoch),
      "ct_alive" = mean(sim_fw$ct_alive),
      "avg_int_strength" = mean(sim_fw$avg_int_strength),
      "c" = mean(sim_fw$c),
      "w_avg_tlvl" = mean(sim_fw$w_avg_tlvl),
      "Z" = mean(sim_fw$Z)
    )
  ),
  tar_target(pred_stab_comp_resp_div,
    fixed_effect_fw_stab_comp %>%
      left_join(
        list(
          response = fixed_effect_fw_stab_comp$response,
          variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive")
          ) %>%
        expand.grid() %>%
        left_join(
          tibble(
            variable = c("avg_int_strength", "w_avg_tlvl", "ct_alive"),
            values = list(
              seq(quantile(sim_fw$avg_int_strength)["25%"], quantile(sim_fw$avg_int_strength)["75%"], length.out = 50),
              seq(quantile(sim_fw$w_avg_tlvl)["25%"], quantile(sim_fw$w_avg_tlvl)["75%"], length.out = 50),
              seq(quantile(sim_fw$ct_alive)["25%"], quantile(sim_fw$ct_alive)["75%"], length.out = 50)
            )
          )
        )
        ) %>%
    mutate(slope = pmap(
        list(
          param_name = variable,
          param_values = values,
          coeff = fix_effect
          ),
        function(param_name, param_values, coeff) {
          param <- list(
            seq(0, 1, length.out = length(param_values)),
            param_values
          )
          names(param) <- c("resp_div", param_name)
